### 2008-12-05 doc/sec/Sec_paper.tex
More sections of the sec doc

% This file was converted to LaTeX by Writer2LaTeX ver. 0.5
% see http://www.hj-gym.dk/~hj/writer2latex for more info
\documentclass{article}
\usepackage[ascii]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{amsmath,amssymb,amsfonts,textcomp}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{pdftex, colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, pagecolor=blue, urlcolor=blue, pdftitle=, pdfauthor=qiangwz, pdfsubject=, pdfkeywords=}
\usepackage[pdftex]{graphicx}
% List styles
\newcommand\liststyleLi{%
\renewcommand\theenumi{\arabic{enumi}}
\renewcommand\theenumii{\arabic{enumii}}
\renewcommand\theenumiii{\arabic{enumiii}}
\renewcommand\theenumiv{\arabic{enumiv}}
\renewcommand\labelenumi{\theenumi.}
\renewcommand\labelenumii{\theenumii.}
\renewcommand\labelenumiii{\theenumiii.}
\renewcommand\labelenumiv{\theenumiv.}
}
\newcommand\liststyleLii{%
\renewcommand\labelitemi{${\bullet}$}
\renewcommand\labelitemii{${\circ}$}
\renewcommand\labelitemiii{${\blacksquare}$}
\renewcommand\labelitemiv{${\bullet}$}
}
\newcommand\liststyleLiii{%
\renewcommand\labelitemi{${\bullet}$}
\renewcommand\labelitemii{${\circ}$}
\renewcommand\labelitemiii{${\blacksquare}$}
\renewcommand\labelitemiv{${\bullet}$}
}
\newcommand\liststyleLv{%
\renewcommand\theenumi{\arabic{enumi}}
\renewcommand\theenumii{\arabic{enumii}}
\renewcommand\theenumiii{\arabic{enumiii}}
\renewcommand\theenumiv{\arabic{enumiv}}
\renewcommand\labelenumi{\theenumi.}
\renewcommand\labelenumii{\theenumii.}
\renewcommand\labelenumiii{\theenumiii.}
\renewcommand\labelenumiv{\theenumiv.}
}
% Page layout (geometry)
\setlength\paperwidth{8.5in}
\setlength\paperheight{11in}
\setlength\voffset{-1in}
\setlength\hoffset{-1in}
\setlength\topmargin{0.7874in}
\setlength\oddsidemargin{0.7874in}
\setlength\textheight{9.4251995in}
\setlength\textwidth{6.9251995in}
\setlength\footskip{0.0cm}
\setlength\headheight{0cm}
\setlength\headsep{0cm}
% Footnote rule
\setlength{\skip\footins}{0.0469in}
\renewcommand\footnoterule{\vspace*{-0.0071in}\setlength\leftskip{0pt}\setlength\rightskip{0pt plus 1fil}\noindent\textcolor{black}{\rule{0.25\columnwidth}{0.0071in}}\vspace*{0.0398in}}
% Pages styles
\makeatletter
\newcommand\ps@Standard{
  \renewcommand\@oddhead{}
  \renewcommand\@evenhead{}
  \renewcommand\@oddfoot{}
  \renewcommand\@evenfoot{}
  \renewcommand\thepage{\arabic{page}}
}
\makeatother
\pagestyle{Standard}
\title{}
\begin{document}
{\centering
Towards cross-domain authentication and standardized attribute-based
authorization for ARC grid middleware
\par}

@@

\ In order to make the access to Grids as simple as possible, security
including authentication and authorization is one of the most important
challenges in production Grids, especially when the Grid applications
are across multiple administration domains as well as across
heterogeneous Grid middlewares, such as some widely scaled eScience
applications which needs to coordinate resources sharing among
collection of autonomous institutions with different Grid middlewares
running on these resources. In this paper, we describe the security
implementation and consideration in new version of Advanced Resource
Connector (ARC) middleware, where the above issues have been exploited.
The main goal of ARC implementation in terms of security is to let the
middleware be capable to \ interoperate with other Grid middlewares by
leveraging standard specifications. The key aspect of the work we have
done is to enhance the current proxy certificate based delegation and
authentication by utilizing the Security Assertion Markup Languages
(\textit{SAML}) single sign-on (SSO) profile, WS-Security in order to
achieve cross-domain authentication, as well as to enhance the
Attribute Certificate (AC) based authorization by utilizing the SAML
\ attribute query profile in order to achieve standardized
attribute-based authorization. \

@@

\ The rest of this paper is organized as follows: Section 2 shows the
ARC grid middleware, especially the architecture if the new version of
ARC. Section 3 describes the solution about cross-domain authentication
and single sign-on is presented, including a few solutions implemented
for bridging the mismatch in terms of authentication. \ Section 4
describes the implementation about standardized attribute querying for
authorization. Section 5 discusses the related research, and Section 6
concludes.

Based on OASIS WS-Trust 1.3 standard

Allows us to bridge security domains in a scalable manner

Allows the use of multiple token formats

pick which is best/supported for your product

Privacy can be protected across applications because:

\ Each application can get a different, opaque, ID

\ Each application receives only the attributes it needs

\ \ \ \ Attributes may be retrieved from places like VOMS, GUMS, etc.

\ \ \ \ When one application requests a token for use with another that
token \ may be encrypted so that only the receiving app may view its
data

The STS serves as a point where policy decisions, such as \ whether App1
can talk to App2, can be made.

Removes the need for proprietary token related protocols

\ \ Supports a superset of current operations and works for more than
\ one token format

While we started our work on the STS in the grid space it \ became clear
it had other uses:

\ \ A portal wants to connect to a SOAP service to get information
\ about you but needs a SAML assertion to do it

\ \ A user wants to connect to an AFS server in a different domain
\ using the credentials from their domain

\ \ A user has a SAML assertion but needs a Kerberos ticket to
\ communicate with SharePoint

There are a number of token formats out there. \ Chances \ are high,
amongst all the software you have, more than one \ format is supported.

How will you prepare for the next greatest format to hit the \ street?

In ARC1, besides that GSI is supported for talking with external grid
services which are based on GSI, the standard TLS/SSL is also
supported.

@@

Two examples of MCC components configuration in Figure 1 shows MCC are
configurable: real line shows SOAP over HTTPS (HTTP over TLS), while
dotted line shows SOAP directly over TCP. Service administrator can
configure the MCCs according to his requirement, such as the
interoperability requirement with the other part. For instance, the
later configuration is compatible to WSE (Web Services Enhancement for
.NET) {\textquotesingle}s SOAP message mechanism (see
WSE{\textquotesingle}s \textit{SoapSender} and \textit{SoapReceiver}).
Another configuration could be SOAP over HTTPG (HTTP over GSI) which
can be user to interoperate with some service based on HTTPG such as
SRM (Storage Resource Manager) [ref] service. The easily configurable
characteristics shows the flexibility of HED in terms of protocol
supporting.

@@

\liststyleLiii
\begin{itemize}
\item \textit{Integration of community authentication} -{}-{}- to
utilize the standardized community authentication from Shibboleth
Identity Provider software when users authenticate against Grid
services.
\item \textit{Short lived credential service} \ {}-{}-{}- to issue the
short lived X.509 certificate for user by using the community
authentication, in order to interoperate with services that depends on
PKI based mutual authentication.
\end{itemize}

@@

\begin{center}
\includegraphics[width=3.398in,height=2.1555in]{Secpaper-img2.png}
\end{center}

@@

\liststyleLv
\begin{enumerate}
\item The client use the user agent interface to launches a http request
including the IdP name (to which the user belongs) to the service side.
The host-name and port of destination URL is the same as that of the
real service, the last part of the destination URL is
{\textquotedblleft}saml2sp{\textquotedblright} which is specific for
pointing to the Service Provider. Note that we use Identity Provider
(IdP) name here to simplify the IdP discovery process, because we
suppose that user who would access the service should better know where
is he from initially.
\item The SP Service (Service Provider) searches the metadata (we use
the same metadata with the same format defined in Shibboleth) and gets
the location of the single sign-on service (hosted in IdP) and also the
location of assertion consuming service (hosted in this SP itself) in
order to compose the SAML {\textless}AuthnRequest{\textgreater}
message. Then SP Service issues this
{\textless}AuthnRequest{\textgreater} message by using its own X.509
certificate (Note in the SAML SSO profile, certificate is still needed
by IdP and SP) and sends back to user agent.
\item User agent sends the {\textless}AuthnRequest{\textgreater} message
to Identity Provider.
\item Identity Provider requires an act of authentication. The
authentication mechanism is outside of the SAML2.0 SSO profile. The
shibboleth IdP implementation will choose some login handler for
authentication. The current user agent implementation is compatible to
the Username/Password login handler of Shibboleth IdP. Through the http
protocol, user agent will feed IdP with the username/password which has
been given by the caller of user agent interface.
\item Once the authentication has been succeeded, the IdP issues a SAML
response including an encrypted (encrypted by destination
SP{\textquotesingle}s public key) SAML assertion, and then this SAML
response will be delivered by the user agent to the Service Provider. 
\item The SP Service verifies and checks the SAML response, and decrypts
and stores the SAML assertion into session/connection context. The SAML
assertion actually includes the {\textless}AuthnStatement{\textgreater}
and {\textless}AttributeStatement{\textgreater}.
\item The WS-Client launches the real Grid/Web Service request via the
same connection as the one which is used by user agent to contacts SP
Service.
\item The Grid/Web Service checks the
{\textless}AuthnStatement{\textgreater} from the session context to see
if the session is still valid through the \textit{SecHandler} called
{\textquotedblleft}SAML SecHandler{\textquotedblright}. And if valid,
service handles the real service processing and returns the response to
WS client. Note that service requires WS client is from the same
connection as the one on which user agent contact SP service in order
to guarantee that the validity of SSO profile result effects the real
client/service interaction.
\end{enumerate}
The SP service and real functional service(s) are hosted by the same
container, and they use the same X.509 credential. The client side
authentication is switched off, so that client doesn{\textquotesingle}t
need to use any X.509 credential. Only the trusted certificates (CA
certificate for SP and IdP) need to be configured for client side so
that SP and IdP can authenticate themselves to the client. As required
by SAML2.0 profile, the SP and IdP should have trust relationship to
each other.

@@

However, the \ \ Based on the solution described in Section 3.1,

@@

\begin{center}
\includegraphics[width=4.2134in,height=3.8972in]{Secpaper-img3.png}
\end{center}
{\centering
Figure 3. Short lived credential service
\par}

@@

how to compose the DN

@@

command line

@@

\ \ 3.3 Certificate delegation service

@@

\ \ 3.4 From transport level security to message level security: X.509
Token and SAML Token

\ \ 3.5 Delegation between WS-Security tokens

{\centering
4. Standardized Attribute-based authorization 
\par}

4.1 SAML Attribute Query profile

4.2 Client to VOMS Attribute authority Service

4.3 Attribute parsing and Policy decision point

{\centering
5. Related work
\par}

VOMS AA Service

@@

@@

{\centering
6. Conclusion and Future work
\par}

@@

>>>>

% This file was converted to LaTeX by Writer2LaTeX ver. 0.5
% see http://www.hj-gym.dk/~hj/writer2latex for more info
\documentclass{article}
\usepackage[ascii]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{amsmath,amssymb,amsfonts,textcomp}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{pdftex, colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, pagecolor=blue, urlcolor=blue, pdftitle=, pdfauthor=qiangwz, pdfsubject=, pdfkeywords=}
\usepackage[pdftex]{graphicx}
% List styles
\newcommand\liststyleLi{%
\renewcommand\theenumi{\arabic{enumi}}
\renewcommand\theenumii{\arabic{enumii}}
\renewcommand\theenumiii{\arabic{enumiii}}
\renewcommand\theenumiv{\arabic{enumiv}}
\renewcommand\labelenumi{\theenumi.}
\renewcommand\labelenumii{\theenumii.}
\renewcommand\labelenumiii{\theenumiii.}
\renewcommand\labelenumiv{\theenumiv.}
}
\newcommand\liststyleLii{%
\renewcommand\labelitemi{${\bullet}$}
\renewcommand\labelitemii{${\circ}$}
\renewcommand\labelitemiii{${\blacksquare}$}
\renewcommand\labelitemiv{${\bullet}$}
}
\newcommand\liststyleLiii{%
\renewcommand\labelitemi{${\bullet}$}
\renewcommand\labelitemii{${\circ}$}
\renewcommand\labelitemiii{${\blacksquare}$}
\renewcommand\labelitemiv{${\bullet}$}
}
\newcommand\liststyleLiv{%
\renewcommand\theenumi{\arabic{enumi}}
\renewcommand\theenumii{\arabic{enumii}}
\renewcommand\theenumiii{\arabic{enumiii}}
\renewcommand\theenumiv{\arabic{enumiv}}
\renewcommand\labelenumi{\theenumi.}
\renewcommand\labelenumii{\theenumii.}
\renewcommand\labelenumiii{\theenumiii.}
\renewcommand\labelenumiv{\theenumiv.}
}
\newcommand\liststyleLv{%
\renewcommand\theenumi{\arabic{enumi}}
\renewcommand\theenumii{\arabic{enumii}}
\renewcommand\theenumiii{\arabic{enumiii}}
\renewcommand\theenumiv{\arabic{enumiv}}
\renewcommand\labelenumi{\theenumi.}
\renewcommand\labelenumii{\theenumii.}
\renewcommand\labelenumiii{\theenumiii.}
\renewcommand\labelenumiv{\theenumiv.}
}
% Page layout (geometry)
\setlength\paperwidth{8.5in}
\setlength\paperheight{11in}
\setlength\voffset{-1in}
\setlength\hoffset{-1in}
\setlength\topmargin{0.7874in}
\setlength\oddsidemargin{0.7874in}
\setlength\textheight{9.4251995in}
\setlength\textwidth{6.9251995in}
\setlength\footskip{0.0cm}
\setlength\headheight{0cm}
\setlength\headsep{0cm}
% Footnote rule
\setlength{\skip\footins}{0.0469in}
\renewcommand\footnoterule{\vspace*{-0.0071in}\setlength\leftskip{0pt}\setlength\rightskip{0pt plus 1fil}\noindent\textcolor{black}{\rule{0.25\columnwidth}{0.0071in}}\vspace*{0.0398in}}
% Pages styles
\makeatletter
\newcommand\ps@Standard{
  \renewcommand\@oddhead{}
  \renewcommand\@evenhead{}
  \renewcommand\@oddfoot{}
  \renewcommand\@evenfoot{}
  \renewcommand\thepage{\arabic{page}}
}
\makeatother
\pagestyle{Standard}
\title{}
\begin{document}
{\centering
Towards cross-middleware authentication and single sign-on for ARC grid
middleware
\par}

@@

\ In order to make the access to Grids as simple as possible, security
is one of the most important challenges in production Grids, especially
when the Grid applications are across multiple administration domains
as well as across heterogeneous Grid middlewares, such as some widely
scaled eScience applications which needs to coordinate resources
sharing among collection of autonomous institutions with different Grid
middlewares running on these resources. In this paper, we describe the
security implementation and consideration in new version of Advanced
Resource Connector (ARC) middleware, where the above issues have been
exploited. The main goal of ARC implementation in terms of security is
to let the middleware be capable to \ interoperate with other Grid
middlewares by leveraging standard specifications. The key aspect of
the work we have done is to enhance the current proxy certificate based
delegation and authentication by utilizing the Security Assertion
Markup Languages (\textit{SAML}) single sign-on (SSO) profile,
WS-Security in order to achieve cross-domain authentication. \

@@

\ The rest of this paper is organized as follows: Section 2 shows the
ARC grid middleware, especially the architecture if the new version of
ARC. Section 3 describes the solution about cross-domain authentication
and single sign-on is presented, including a few solutions implemented
for bridging the mismatch in terms of authentication. Section 4
discusses the related research, and Section 5 concludes.

@@

Two examples of MCC components configuration in Figure 1 shows MCC are
configurable: real line shows SOAP over HTTPS (HTTP over TLS), while
dotted line shows SOAP directly over TCP. Service administrator can
configure the MCCs according to his requirement, such as the
interoperability requirement with the other part. For instance, the
later configuration is compatible to WSE (Web Services Enhancement for
.NET) {\textquotesingle}s SOAP message mechanism (see
WSE{\textquotesingle}s \textit{SoapSender} and \textit{SoapReceiver}).
Another configuration could be SOAP over HTTPG (HTTP over GSI) which
can be used to interoperate with some service based on HTTPG such as
SRM (Storage Resource Manager) [ref] service. The easily configurable
characteristics shows the flexibility of HED in terms of protocol
supporting.

@@

\liststyleLiii
\begin{itemize}
\item \textit{Integration of community authentication} -{}-{}- to
utilize the standardized community authentication from Shibboleth
Identity Provider software when users authenticate against Grid
services.
\item \textit{Short lived credential service} \ {}-{}-{}- to issue the
short lived X.509 certificate for user by using the community
authentication, in order to interoperate with services that depends on
PKI based mutual authentication.
\item \textit{Credential delegation service} -{}-{}- to process the
X.509 credential delegation as a normal Web Service, in order to
provide single sign-on characteristic.
\item \textit{Message level authentication} -{}-{}- to provide message
level authentication by implementing WS-Security.
\item 
\bigskip
\end{itemize}

@@

\begin{center}
\includegraphics[width=3.4063in,height=2.1417in]{Secpaper-img2.png}
\end{center}

@@

\liststyleLiv
\begin{enumerate}
\item The client use the user agent interface to launches a http request
including the IdP name (to which the user belongs) to the service side.
The host-name and port of destination URL is the same as that of the
real service, the last part of the destination URL is
{\textquotedblleft}saml2sp{\textquotedblright} which is specific for
pointing to the Service Provider. Note that we use Identity Provider
(IdP) name here to simplify the IdP discovery process, because we
suppose that user who would access the service should better know where
is he from initially.
\item The SP Service (Service Provider) searches the metadata (we use
the same metadata with the same format defined in Shibboleth) and gets
the location of the single sign-on service (hosted in IdP) and also the
location of assertion consuming service (hosted in this SP itself) in
order to compose the SAML {\textless}AuthnRequest{\textgreater}
message. Then SP Service issues this
{\textless}AuthnRequest{\textgreater} message by using its own X.509
certificate (Note in the SAML SSO profile, certificate is still needed
by IdP and SP) and sends back to user agent.
\item User agent sends the {\textless}AuthnRequest{\textgreater} message
to Identity Provider.
\item Identity Provider requires an act of authentication. The
authentication mechanism is outside of the SAML2.0 SSO profile. The
shibboleth IdP implementation will choose some login handler for
authentication. The current user agent implementation is compatible to
the Username/Password login handler of Shibboleth IdP. Through the http
protocol, user agent will feed IdP with the username/password which has
been given by the caller of user agent interface.
\item Once the authentication has been succeeded, the IdP issues a SAML
response including an encrypted (encrypted by destination
SP{\textquotesingle}s public key) SAML assertion, and then this SAML
response will be delivered by the user agent to the Service Provider. 
\item The SP Service verifies and checks the SAML response, and decrypts
and stores the SAML assertion into session/connection context. The SAML
assertion actually includes the {\textless}AuthnStatement{\textgreater}
and {\textless}AttributeStatement{\textgreater}.
\item The WS-Client launches the real Grid/Web Service request via the
same connection as the one which is used by user agent to contacts SP
Service.
\item The Grid/Web Service checks the
{\textless}AuthnStatement{\textgreater} from the session context to see
if the session is still valid through the \textit{SecHandler} called
{\textquotedblleft}SAML SecHandler{\textquotedblright}. And if valid,
service handles the real service processing and returns the response to
WS client. Note that service requires WS client is from the same
connection as the one on which user agent contact SP service in order
to guarantee that the validity of SSO profile result effects the real
client/service interaction.
\end{enumerate}
The SP service and real functional service(s) are hosted by the same
container, and they use the same X.509 credential. The client side
authentication is switched off, so that client doesn{\textquotesingle}t
need to use any X.509 credential. Only the trusted certificates (CA
certificate for SP and IdP) need to be configured for client side so
that SP and IdP can authenticate themselves to the client. As required
by SAML2.0 profile, the SP and IdP should have trust relationship to
each other.

One benefit of SAML2.0 SSO profile that is worth mentioning is that: the
Identity Provider could cache the authentication result through session
management once the user agent has succeeded to authenticate, then in a
short period this authentication result is valid so that user agent
don{\textquotesingle}t need to feed IdP with user{\textquotesingle}s
username and password the next time (if the time is not out of the
scope of valid period) it authenticates against IdP. So user (or the
client on behalf of this user) can travel across multiple security
domains with only inputing his name and password once, which is the
characteristic of single sign-on.

@@

However, most of the widely used grid middlewares are based on GSI while
GSI requires mutual authentication. Also for Web Service based grid
solution, we can not prevent service side from requiring client X.509
certificate. \ Based on the solution described in Section 3.1, we
implemented a short lived credential service (SLCS) by which user can
get a short-lived X.509 certificate without being bothered to contact
any registration authority (RA) or certificate authority (CA).

The SLCS service is actually a specific Web Service (standard web
service implemented by using ARC service interface) in Figure 2, and
the SLCS client is a specific ARC client which includes the user agent
and WS client. The whole process from step 1 to step 8 is the same as
in Figure 2.

@@

\begin{center}
\includegraphics[width=3.7689in,height=3.2055in]{Secpaper-img3.png}
\end{center}
{\centering
Figure 3. Short lived credential service
\par}

\ \ \ SLCS client generates a X.509 certificate request, launches a Web
Service request which includes the certificate request; SLCS service
then gets the certificate request, composes a distinguished name (DN),
issues a certificate (short lived, 12 hours by default) with the SAML
attribute (from the SAML2.0 SSO profile) as the X.509 certificate
extension, and puts the certificate in to the Web Service response;
SLCS client get the response and stores the X.509 certificate into
local repository.

The command line interface for the SLCS client is like this:

\$ ./arcslcs -S https://127.0.0.1:60000/slcs -I
https://idp.testshib.org/idp/shibboleth -U myself -P myself

\ \ \ Since the lifetime of the short lived credential is normally
short, it is not a must to protect the private key by pass-phrase. As
illustrated in step a and step b in Figure 3, if the private key is not
protected, through Web Service client, the user can use the X.509
certificate to access Grid Service or Web Service from any kind of
middleware. If the private key is protected, the can use the X.509
certificate to generate a proxy certificate (by using command line
interface utility such as \textit{grid-proxy-init},
\textit{voms-proxy-init}, or \textit{arcproxy}), and the use the proxy
certificate to access Grid Service or Web Service.

\ \ \ It is worth mentioning that since ARC middleware can support GSI
communication by configuring the GSI MCC, \ together with the X.509
certificate, the Web Service client developed by ARC client interface
can interoperate with Grid Service that requires GSI communication.

\ \ \ It might be noticed that how to compose the distinguished name
(DN) for the certificate is critical issue for SLCS service. Since the
Shibboleth Identity Provider uses the eduPerson schema [ref] for the
definition of {\textless}saml:Attribute{\textgreater} in
{\textless}saml:AttributeStatement{\textgreater}, we pick the
relatively distinguishable attribute
{\textquotedblleft}eduPersonPrincipalName{\textquotedblright} for the
DN. A typical \ eduPersonPrincipalName \ value could be
\href{mailto:alice@example.org}{alice@example.org}, then the DN is
{\textquotedblleft}/O=knowarc/OU=example.org/CN=alice{\textquotedblright}.

The obvious benefit of SLCS service is that: If a user passes the
authentication to his home Identity Provider, he can get the X.509
credential at anywhere only by running the SLCS client command together
with inputing his username and password to this home IdP, and then
access the grid system conveniently; meanwhile, thanks to the single
sign-on characteristic discussed in Section 3.1, this user
\ doesn{\textquotesingle}t not need to input his username and password
in a valid period after the first time he succeeds to authenticate
against his home IdP by running the SLCS client command on the same
node, even if this SLCS client command is supposed to run against a few
SLCS services to get a few SLCS credentials.

@@

\ \ 3.3 X.509 Credential delegation service

The delegation of credentials proposed in Grid Security Infrastructure
(GSI) is a good solution for the supporting of single sign-on for
users, except the coupling of the GSI communication which is not so
widely accepted in Web Service applications. In the design of the new
version ARC middleware, we keep the credential delegation idea, while
utilizing the SOAP communication (and normal TCP or TLS for transport
level communication) instead of the GSI communication for the
credential delegation process.

As shown in Figure 4, there is a specific WS client and Web Service as
well for processing delegation: delegation client, and delegation
service. The delegation service has two main wsdl operations, one for
processing the delegation initiation; the other for processing/storing
the signed proxy certificate. The delegation process is detailed in
Figure 5.

For the service invocation process, the WS client functionality (inside
each service or the initial client) which is included to access the
target service (step a1 or a2 in Figure 4), should use the
user{\textquotesingle}s X.509 certificate or proxy certificate (on
behalf of the user) for authentication and secure communication. For
the delegation process, the principle is the same.

Since each WS client accesses the target service (delegation service or
other functional service) on behalf of the user, the trust relationship
between the user{\textquotesingle}s certificates (X.509 certificate and
proxy certificate) and services is required, while the trust
relationship between service and service is not required.

\begin{center}
\includegraphics[width=3.802in,height=3.0689in]{Secpaper-img4.png}
\end{center}

@@

{\centering
Figure 4. Credential delegation service
\par}

\begin{center}
\includegraphics[width=2.5319in,height=1.8571in]{Secpaper-img5.png}
\end{center}
{\centering
Figure 5. Credential delegation process
\par}

\ \ 3.4 Message level authentication

Transport level security (TLS or SSL) is not sufficient for securing Web
Services, because the secure channel created by SSL/TLS make it
impossible to differentially protect the SOAP message, e.g. \ to
encrypt and/or sign only particular components of the SOAP message,
which is relevant when non-sensitive portions of the message need to be
accessed or changed by intermediate actors. Additionally, SSL/TLS is
incapable of providing end-to-end protection for SOAP message which
might flow through multiple intermediate actors, because it only allows
each hop to be protected with the resultant security gaps at
intermediate actors. Web Services Security (WS-Security) specification
(ref) provides means for applying security to Web Service.

The WS-Security related specifications are implemented in ARC as
\textit{SecHandler}. There are three kinds of WS-Security version 1.1
specifications are completely or partly implemented: Username Token
profile, X.509 Token profile, and SAML Token profile.

For those WS clients on behalf of a user, at any step of service
invocation, the WS client can augment the SOAP message with WS-Security
token by simply configuring the WS-Security \textit{SecHandler} into
container{\textquotesingle}s configuration, if the relying party
(target service) requires.

If the WS client owns an X.509 certificate or proxy certificate, the
process of generating an X.509 Token for a SOAP message is: the client
puts the content of certificate into X.509 token as
{\textless}wsse:BinarySecurityToken{\textgreater}, and uses the private
key (corresponding to the certificate) to create XML signature for the
SOAP message body.

However the process of generating a SAML Token is more complicated. In
SAML Token profile, \textit{ConfirmationMethod} is the verifying method
for establishing proof-of-possession for the subject. Two methods are
proposed in SAML Token profile: \textit{holder-of-key},
\textit{sender-vouches}. \ We rely on the \textit{holder-of-key
}method. For the \textit{hold-of-key} subject confirmation method,
there are three interaction parts: the attesting entity, the relying
party and the issuing authority. Firstly the attesting entity
authenticates to issuing authority by using some authentication scheme
such as X.509 Token profile. So then issuing authority is able to make
a definitive statement (sign a SAML assertion) about an act of
authentication that has already taken place. The attesting entity gets
the SAML assertion and then signs the SOAP message together with the
assertion by using its private key (the relevant certificate has been
authenticated by issuing authority, and its relevant public key has
been put into \textit{SubjectConfirmation}

element under SAML assertion by issuing authority. Only the actual owner
of the SAML assertion can do this, as only the subject possesses the
private key paired with the public key in the assertion. This
establishes an irrefutable connection between the author of the SOAP
message and the assertion describing an authentication event.)

\ The relying party is supposed to trust the issuing authority. When it
receives a message from the asserting entity, it will check the SAML
assertion based on its predetermined trust relationship with the SAML
issuing authority, and check the signature of the soap message based on
the public key in the SAML assertion without directly trust
relationship with attesting entity (subject owner).

\ \ 3.5 SAML Token delegation service

\ There is also delegation requirement on the message level, some
entities (client or user) often need to temporarily delegate itself to
another entity to perform action on their behalf. We propose a
delegation mechanism for SAML Token.

The delegation process is similar to the process for delegation proxy
certificate, with the following differences:

\liststyleLv
\begin{enumerate}
\item The communication between delegation client and service is based
on mutual authentication between proxy certificate and service
certificate, instead, it is based on mutual authentication between
service certificate and service certificate.
\item The delegation service will not generate any certificate request,
instead, it picks the public key from its own service certificate, and
sends back to delegation client.
\end{enumerate}
Figure 6 shows the token change due to delegation. On the left side, B
is the identity of the attesting entity{\textquotesingle}s X509 token
mentioned above, while A is the identity of issuing authority, and the
SOAP message is signed by B{\textquotesingle}s private key. On the
right side, C is the identity of the delegation service, ans now the
SOAP message is signed by C{\textquotesingle}s private key.

\begin{center}
\includegraphics[width=4.2571in,height=2.152in]{Secpaper-img6.png}
\end{center}
{\centering
\ \ \ \ \ \ \ \ \ Figure 6. Token before and after delegation
\par}

@@

@@

{\centering
4. Related work
\par}

@@

Delegation service : gridsite

@@

{\centering
5. Conclusion and Future work
\par}

@@

eduPerson and eduOrg Object shema.
\url{http://middleware.internet2.edu/eduperson/}
